Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-20 paper/aldebaran.tex
wording

Using the \textsc{k2ps} planet-search code \citep{k2ps,Pope2016} to examine this light curve, we search for transits across a wide range of periods, and find no evidence either of planetary transits or an eclipsing stellar companion.

>>>>

Using the \textsc{k2ps} planet-search code \citep{k2ps,Pope2016} to examine this light curve, we search for transits across a wide range of periods, and find no evidence either of short-period planetary transits or an eclipsing stellar companion.
